Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
No 'real' data

```{r}
# Bring data --------------------------------------------
load("Ch1_movement_rates/sims_backup/datagen_cp.RData")
load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
load("Ch1_movement_rates/sims_backup/datagen_np.RData")
#load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")

load("Ch1_movement_rates/sims_backup/weib_cp.RData")
load("Ch1_movement_rates/sims_backup/weib_pp.RData")
load("Ch1_movement_rates/sims_backup/weib_np.RData")
#load("Ch1_movement_rates/sims_backup/weib_ppi.RData")

# Real data --------------------------------------
load("Ch1_movement_rates/sims_backup/datagen_cpr.RData")
load("Ch1_movement_rates/sims_backup/datagen_ppr.RData")
load("Ch1_movement_rates/sims_backup/datagen_npr.RData")

load("Ch1_movement_rates/sims_backup/weib_cpr.RData")
load("Ch1_movement_rates/sims_backup/weib_ppr.RData")
load("Ch1_movement_rates/sims_backup/weib_npr.RData")

>>>>

```{r}
# Bring data --------------------------------------------
load("Ch1_movement_rates/sims_backup/datagen_cp.RData")
load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
load("Ch1_movement_rates/sims_backup/datagen_np.RData")

load("Ch1_movement_rates/sims_backup/weib_cp.RData")
load("Ch1_movement_rates/sims_backup/weib_pp.RData")
load("Ch1_movement_rates/sims_backup/weib_np.RData")
